---
title: "Exercises Chapter 2"
author: "Semiramis Castro-Jaimes"
date: "20 de abril de 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1014)
library(lobstr)
```

## Explain the relationship between a, b, c and d in the following code:
```{r}
a <- 1:10
b <- a
c <- b
d <- 1:10
```

```{r}
res<-c(obj_addr(a), obj_addr(b), obj_addr(c), obj_addr(d))
names(res)<-c("a", "b", "c", "d")
res
```
a, b y c apuntan a la misma dirección de memoria


## The following code accesses the mean function in multiple ways. Do they all point to the same underlying function object? Verify this with lobstr::obj_addr()
```{r eval=FALSE}
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```

```{r}
res<-c(obj_addr(mean), 
       obj_addr(base::mean),
       obj_addr(get("mean")), 
       obj_addr(evalq(mean)), 
       obj_addr(match.fun("mean"))
)
res

```
Oooohhh, todas sí hacen referencia a la misma dirección de memoria


## By default, base R data import functions, like read.csv(), will automatically convert non-syntactic names to syntactic ones. Why might this be problematic? What option allows you to suppress this behaviour?
A: This might be problematic when we have special caracters. We can suppress this behavior with check.names


## What rules does make.names() use to convert non-syntactic names into syntactic ones?
A: From the function documentation: 'The character "X" is prepended if necessary. All invalid characters are translated to ".". A missing value is translated to "NA". Names which match R keywords have a dot appended to them. Duplicated values are altered by make.unique.'

## I slightly simplified the rules that govern syntactic names. Why is .123e1 not a syntactic name? Read ?make.names for the full details.

A: Because it starts with a dot. It will be prepended with an X:
```{r}
make.names(.123e1)
```

```{r}
l1 <- list(1, 2, 3)
l2 <- l1
l2[[3]] <- 4
ref(l1, l2)
```

## Why is tracemem(1:10) not useful?

A: Porque no es un nombre de objeto


## Explain why tracemem() shows two copies when you run this code. Hint: carefully look at the difference between this code and the code shown earlier in the section.
```{r}
x <- c(1L, 2L, 3L)
tracemem(x)
x[[3]] <- 4
```
 Supuse que porque se transforma a una lista, pero no
 Igual y porque accedemos directamente a la dirección de memoria del elemento 3 en lugar de su valor
```{r}
ref(x, x[[3]], x[1], x[2], x[3])
```
 

## Sketch out the relationship between the following objects:
```{r}
a <- 1:10
b <- list(a, a)
c <- list(b, a, 1:10)
```

```{r}
ref(a, b, c)
```

## What happens when you run this code?
```{r}
tracemem(x)
```

```{r}
x <- list(1:10)
tracemem(x)
x[[2]] <- x
```

```{r}
ref(x)
```


## In the following example, why are object.size(y) and obj_size(y) so radically different? Consult the documentation of object.size().
```{r}
y <- rep(list(runif(1e4)), 100)
object.size(y)
```
```{r}
obj_size(y)

```
A: porque object.size() no toma en cuenta los elementos compartidos, y asume que todos los elementos están contiguos


## Take the following list. Why is its size somewhat misleading?
```{r}
funs <- list(mean, sd, var)
obj_size(funs)
```
A: Porque la lista tiene la referencia de memoria a las referencias de memoria de cada función enlistada


## Predict the output of the following code:
```{r}
a <- runif(1e6)
obj_size(a)

b <- list(a, a)
obj_size(b)
obj_size(a, b)

b[[1]][[1]] <- 10
obj_size(b)
obj_size(a, b)

b[[2]][[1]] <- 10
obj_size(b)
obj_size(a, b)

```
A: Al principio había elementos compartidos, así que pesaban lo mismo, pero con cada modificación dejaron de compartir elementos, y en lugar de apuntar a direcciones de memoria, los elementos de b guardaron valores


## Explain why the following code doesn’t create a circular list.
```{r}
x <- list()
tracemem(x)
x[[1]] <- x

```
Porque se crea una copia de la lista cuando ésta se modifica


