---
title: "Exercises Chapter 3"
author: "Semiramis Castro-Jaimes"
date: "21 de abril de 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1014)
```

1. Test your knowledge of the vector coercion rules by predicting the output of the following uses of c():
```{r}
c(1, FALSE)
c("a", 1)
c(TRUE, 1L)

```
A: c(1, 1); c("a","1"); c(1L, 1L)



2. Why is 1 == "1" true? Why is -1 < FALSE true? Why is "one" < 2 false?
A: Because: numeric is coerced into string; logical into numeric; numeric into string and numbers come before letters when sorted as string

3. Why is the default missing value, NA, a logical vector? What’s special about logical vectors? (Hint: think about c(FALSE, NA_character_).)
A: because NAs should not change the type of the object, and logicals can be coerced into the other data types



1. Can you have a data frame with zero rows? What about zero columns?
```{r}
a<-data.frame()
dim(a)
```


2. What happens if you attempt to set rownames that are not unique?
```{r}
df<-data.frame(A=letters[1:4], B=letters[2:5])
rownames(df)<-c(letters[1:3], "a")
```


3. If df is a data frame, what can you say about t(df), and t(t(df))? Perform some experiments, making sure to try different column types.
```{r}
df<-data.frame(soup=letters[1:4], 
               nums=seq_len(4),
               integers=c(10L, 20L, 30L, 40L),
               decimals=c(50.5, 60.5, 75.5, 80.8),
               words=month.abb[5:8],
               times=c(as.Date("2018-08-01", tz = "GTM"),
                       as.Date("2019-08-01", tz = "UTC"),
                       as.Date("1970-02-01", tz = "UTC"),
                       as.Date("1980-02-01", tz = "GTM")
                       )
)

head(df)

```

```{r}
head(t(df))
```
A: Se perdieron los tipos de dato que no eran letras/palabras; todo fue convertido a character


4. What does as.matrix() do when applied to a data frame with columns of different types? How does it differ from data.matrix()?
```{r}
as.matrix(df)
```
A: Todo se convirtió a character

```{r}
data.matrix(df)
```
A: Todo se convirtió a numeric


