---
title: "Quizz Chapter 3"
author: "Semiramis Castro-Jaimes"
date: "21 de abril de 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1014)
```

1. What are the four common types of atomic vectors? What are the two rare types?
A: Common types: logical, character, integer & double (numeric); Rare: complex and raw


2. What are attributes? How do you get them and set them?
A: Attributes are special characteristics that can change the behavior of the objects. 
```{r}
df<-data.frame(A= as.factor(letters[1:4]),
               B= runif(4))

df
```

We can get attributes with:
```{r}
attr(df, "names")
```
```{r}
attributes(df)
```
```{r}
str(df)
```


We can set attributes with:
```{r}

```



3. How is a list different from an atomic vector? How is a matrix different from a data frame?
A1: a list can have different items; atomic vectors can only hold a data type. Lists store references to the objects, not the elements per se.
A2: A matrix is a 2-D object with rows and columns in which all elements are of the same type; data.frames can have columns with distinct data types and their rows and columns are not interchangeable / transposable


4. Can you have a list that is a matrix? Can a data frame have a column that is a matrix?
A1: Yes, we can embed a matrix into a list
A2: Yes if all columns are also matrices


5. How do tibbles behave differently from data frames?
A: tibbles "complain more and do less"
Tibbles don't convert strings as factors; tibbles don't support row.names

