---
title: "Chapter 10 Exercises"
author: "Semiramis Castro-Jaimes"
date: "4/8/2020"
output: html_document
---

## Base R contains two function factories, approxfun() and ecdf(). Read their documentation and experiment to figure out what the functions do and what they return.
```{r}
approxfun
```

## Create a function pick() that takes an index, i, as an argument and returns a function with an argument x that subsets x with i.
```{r}
i<-2
pick <- function(i) {
  #force(i)
  function(x) x[[i]]
}
x <- 1:3
identical(x[[1]], pick(1)(x))
```

## What happens if you use <- instead of <<-? Make predictions, then verify with the code below.
With `<-` we don't modify the outer variable, whereas with superassignment we do
```{r}
new_counter3 <- function() {
  i <- 0
  function() {
    i <- i + 1
    i
  }
}
new_counter3()()
```

## In boot_model(), why don’t I need to force the evaluation of df or model?
```{r}
boot_model <- function(df, formula) {
  mod <- lm(formula, data = df)
  fitted <- unname(fitted(mod))
  resid <- unname(resid(mod))
  rm(mod)
  function() {
    fitted + sample(resid)
  }
}
```

Because the variables from the inner function are read from its parent environment, and those variables are declared in that parent environment

## Why might you formulate the Box-Cox transformation like this?
```{r}
boxcox3 <- function(x) {
  function(lambda) {
    if (lambda == 0) {
      log(x)
    } else {
      (x ^ lambda - 1) / lambda
    }
  }  
}
```
Because tThis allows us to apply and test different transformations for different inputs and give them a descriptive name."

## Why don’t you need to worry that boot_permute() stores a copy of the data inside the function that it generates?
```{r}
boot_permute <- function(df, var) {
  n <- nrow(df)
  force(var)
  function() {
    col <- df[[var]]
    col[sample(n, replace = TRUE)]
  }
}
boot_mtcars1 <- boot_permute(mtcars, "mpg")
```
Because the environment of the inner function exists only during its execution and when it finishes, its environment is destroyed
Also, we are giving it a pointer to the data, not the data itself

## How much time does `ll_poisson2()` save compared to `ll_poisson1()`? Use `bench::mark()` to see how much faster the optimisation occurs. How does changing the length of xchange the results?
```{r}
# Definition of ll_poisson1 and ll_poisson2 
ll_poisson1 <- function(x) {
  n <- length(x)
  function(lambda) {
    log(lambda) * sum(x) - n * lambda - sum(lfactorial(x))
  }
}
ll_poisson2 <- function(x) {
  n <- length(x)
  sum_x <- sum(x)
  c <- sum(lfactorial(x))
  function(lambda) {
    log(lambda) * sum_x - n * lambda - c
  }
}
```
```{r}
# provided test data
x1 <- c(41, 30, 31, 38, 29, 24, 30, 29, 31, 38)
bench::mark(
  llp1 = optimise(ll_poisson1(x1), c(0, 100), maximum = TRUE),
  llp2 = optimise(ll_poisson2(x1), c(0, 100), maximum = TRUE)
)
```
We get an improvement in performance with the second function factory because the costly operation (lfactorial) is done only once and its re-used in each function created downstream
