---
title: "Exercises Chapter 9"
author: "Semiramis Castro-Jaimes"
date: "22/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(purrr)
```
## Use as_mapper() to explore how purrr generates anonymous functions for the integer, character, and list helpers.
```{r}
as_mapper(c(1,2))
```
```{r}
as_mapper(c("hi", "there"))
```
```{r}
as_mapper(list(c(1,2), c("hi", "there")))
```

A: as_mapper() creates an "extractor" function by calling purrr::pluck()
Note: pluck() returns NULL when an element does not exist.

## `map(1:3, ~ runif(2))` is a useful pattern for generating random numbers, but `map(1:3, runif(2))` is not. Why not? Can you explain why it returns the result that it does?
```{r}
map(1:3, ~ runif(2))
```
Here, we ran three times runif(n=2) so we had two random numbers in each iteration.
"Internally map() applies as_mapper() to this formula, which converts ~ runif(2) into an anonymous function."


```{r}
map(1:3, runif(2))
```
A: Here, runif(2) is evaluated once, and pluck() tries to map its values to the indexes, but pluck() returned NULL each time "because no values corresponding to the index can be found"


## Use the appropriate `map()` function to:
### -Compute the standard deviation of every column in a numeric data frame.
```{r}
df <- data.frame(col1=runif(5), col2=runif(5), col3=runif(5))
map_dbl(df, sd)
```

### -Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to do it in two steps.)
```{r}
df <- data.frame(col1=runif(5), col2=runif(5), col3=runif(5),    
                 col4=letters[1:5], col5=LETTERS[1:5], 
                 stringsAsFactors = FALSE)
selected_columns = map_lgl(df, is.numeric) 
map_dbl(df[,selected_columns], sd)

```

### -Compute the number of levels for every factor in a data frame.
```{r}
df <- data.frame(f1=c(letters[6:10], letters[4:8]),  
                 f2=c(LETTERS[10:14], LETTERS[13:17]),
                 stringsAsFactors = TRUE)
map_int(df, nlevels)
```


## The following code simulates the performance of a t-test for non-normal data. Extract the p-value from each test, then visualise.
```{r}
trials <- map(1:100, ~ t.test(rpois(10, 10), rpois(7, 10)))
str(trials[[1]])
```
```{r}
hist(trials %>% map_dbl("p.value"))
```

## The following code uses a map nested inside another map to apply a function to every element of a nested list. Why does it fail, and what do you need to do to make it work?

```{r}
x <- list(
  list(1, c(3, 9)),
  list(c(3, 6), 7, c(4, 7, 6))
)

triple <- function(x) x * 3
```
```{r eval=FALSE}
map(x, map, .f = triple)
#Error in .f(.x[[i]], ...) : unused argument (map)

```
```{r}
map(x, map, triple)
```
We needed to omit the .f argument because it was interpreted as if it was the argument to the first map instead of the nested map


## Use map() to fit linear models to the mtcars dataset using the formulas stored in this list:
```{r}
formulas <- list(
  mpg ~ disp,
  mpg ~ I(1 / disp),
  mpg ~ disp + wt,
  mpg ~ I(1 / disp) + wt
)
```
```{r}
results <- map(formulas, lm, data=mtcars) 
results
```


## Fit the model mpg ~ disp to each of the bootstrap replicates of mtcars in the list below, then extract the R2 of the model fit (Hint: you can compute the R2 with summary().)
```{r}
bootstrap <- function(df) {
  df[sample(nrow(df), replace = TRUE), , drop = FALSE]
}

bootstraps <- map(1:10, ~ bootstrap(mtcars))
```

```{r}
map(bootstraps, ~lm(mpg ~ disp, data=.x)) %>% 
  map(summary)  %>% 
  map_dbl("r.squared")
```


## Explain the results of modify(mtcars, 1).
```{r}
modify(mtcars, 1)
```
We get the first row again and again for each row (n=32), and we get a data.frame because the input was a data.frame0


## Explain how the following code transforms a data frame using functions stored in a list.
```{r}
trans <- list(
  disp = function(x) x * 0.0163871,
  am = function(x) factor(x, labels = c("auto", "manual"))
)

nm <- names(trans)
mtcars[nm] <- map2(trans, mtcars[nm], function(f, var) f(var))
head(mtcars[nm])
```
We apply the functions in the list 'trans' for each element in mtcars using an anonymous function. We use map2() because we give two arguments onto which we will iterate: trans and mtcars[nm]


## Compare and contrast the map2() approach to this map() approach:
```{r}

mtcars[nm] <- map(nm, ~ trans[[.x]](mtcars[[.x]]))
head(mtcars[nm])
```
Here we use the dot arguments and the function syntax: for each element in trans, we apply that function on each element of mtcars


## What does write.csv() return? i.e. what happens if you use it with map2() instead of walk2()
```{r}
a<- write.csv(mtcars, file = "foo.csv", fileEncoding = "UTF-16LE")
a
```
It returns NULL. If we use map2(), we would get a list of NULLs

## Why isn’t is.na() a predicate function? What base R function is closest to being a predicate version of is.na()?
It is not a predicate function because it does not return a single TRUE/FALSE value; it returns a logical vector of the same size as the input vector.


## simple_reduce() has a problem when x is length 0 or length 1. Describe the source of the problem and how you might go about fixing it.
```{r eval=FALSE}
simple_reduce <- function(x, f) {
  out <- x[[1]]
  for (i in seq(2, length(x))) {
    out <- f(out, x[[i]])
  }
  out
}
simple_reduce(c(1), sum)
#Error in x[[i]] : subíndice fuera de  los límites

```
```{r}
simple_reduce2 <- function(x, f) {
  out <- x[[1]]
  if (length(x) < 2) return("The input must have at least two elements")
  for (i in seq(2, length(x))) {
    out <- f(out, x[[i]])
  }
  out
}
simple_reduce2(c(1), sum)

```
We neeeded to add an if statement to check the length of the input vector because the loop starts from the second element


## Implement the span() function from Haskell: given a list x and a predicate function f, span(x, f) returns the location of the longest sequential run of elements where the predicate is true. (Hint: you might find rle() helpful.)



## Implement arg_max(). It should take a function and a vector of inputs, and return the elements of the input where the function returns the highest value. For example, arg_max(-10:5, function(x) x ^ 2) should return -10. arg_max(-5:5, function(x) x ^ 2) should return c(-5, 5). Also implement the matching arg_min() function.



## The function below scales a vector so it falls in the range [0, 1]. How would you apply it to every column of a data frame? How would you apply it to every numeric column in a data frame?
```{r}
scale01 <- function(x) {
  rng <- range(x, na.rm = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}
```

