---
title: "Exercises Chapter 18"
author: "Semiramis Castro-Jaimes"
date: "17/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rlang)
library(lobstr)
```

## Reconstruct the code represented by the trees below
```{r}
lobstr::ast(
  f(
    g(h()), 1+2+3, (x+y) * z
  )
)
```

## What’s happening with the ASTs below?
They are written in prefix form
```{r}
lobstr::ast(`x` + `y`); lobstr::ast(x ** y); lobstr::ast(1 -> x)
```

## What does the call tree of an if statement with multiple else if conditions look like? Why?
```{r}
lobstr::ast(
  if(x > 10){
    ...
  }else if(x%%2 == 0){
    ...
  }else if(x * 50 < 35){
    ...
  }
)
```
Because each condition is composed by one or more function calls; those functions are either comparison operators alone or comparison and arithmetic operators 


## What happens when you subset a call object to remove the first element? e.g.
```{r}
expr(read.csv("foo.csv", header = TRUE))[-1]
```
The second element becomes the function's name because the first element of an expression is always the function to be called


## rlang::call_standardise() doesn’t work so well for the following calls. Why? What makes mean() special?
```{r eval=FALSE}
call_standardise(quote(mean(1:10, na.rm = TRUE)))
#> mean(x = 1:10, na.rm = TRUE)
call_standardise(quote(mean(n = T, 1:10)))
#> mean(x = 1:10, n = T)
call_standardise(quote(mean(x = 1:10, , TRUE)))
#> mean(x = 1:10, , TRUE)
```
```{r}
mean
```
call_standardize() does not go well with ... arguments, and the second argument of mean is ...


## Construct the expression if(x > 1) "a" else "b" using multiple calls to call2(). How does the code structure reflect the structure of the AST?
```{r}
call2("if", 
      call2(">", expr(x), 1), "a", "b"
)
```
```{r}
lobstr::ast(if(x > 1) "a" else "b")
```
They are very similar

## What happens if you call parse_expr() with a string that generates multiple expressions? 
```{r eval=FALSE}
parse_expr("x + 1; y + 1")
# Error: More than one expression parsed
```
It throws an error; for multiple expressions we use parse_exprs()
```{r}
parse_exprs("x + 1; y + 1")
```







