---
title: "Exercises Chapter 19"
author: "Semiramis Castro-Jaimes"
date: "22/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## How is expr() implemented? Look at its source code.
```{r}
expr
```
It's a call to enexpr()


## Compare and contrast the following two functions. Can you predict the output before running them?
```{r}
f1 <- function(x, y) {
  exprs(x = x, y = y)
}
f1(a + b, c + d)
```
The output would have the symbols used in the function definition: x and y instead of the original expression


```{r}
f2 <- function(x, y) {
  enexprs(x = x, y = y)
}
f2(a + b, c + d)
```
In this other case, the output would reflect the original expression


## What happens if you try to use enexpr() with an expression (i.e.  enexpr(x + y) ? 
```{r eval=FALSE}
enexpr(x + y)
```
It throws an error because the function expects a symbol


## Given the following components:
```{r}
xy <- expr(x + y)
xz <- expr(x + z)
yz <- expr(y + z)
abc <- exprs(a, b, c)
```

## Use quasiquotation to construct the following calls:
```{r eval=FALSE}
(x + y) / (y + z)
-(x + z) ^ (y + z)
(x + y) + (y + z) - (x + y)
atan2(x + y, y + z)
sum(x + y, x + y, y + z)
sum(a, b, c)
mean(c(a, b, c), na.rm = TRUE)
foo(a = x + y, b = y + z)
```

```{r}
expr(!!xy / !!xz)
```
```{r}
expr(- (!!xz) ^( !!yz))
```

```{r}
expr(!!xy + !!yz - (!!xy))

```

```{r}
expr(atan(!!xy, !!yz))
```

```{r}
expr(sum(!!xy, !!xy, !!yz))
```

```{r}
expr(sum(!!!abc))
```

```{r}
expr(mean(c(!!!abc), na.rm = TRUE))
```

```{r}
expr(foo(a = !!xy, b = !!yz))
```


